Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-05-24 doc/paper.Rmd
type 2 errors back in the appendix

```{r type2, fig.height = 3, fig.width = 7.5, out.width='0.9\\textwidth', fig.cap="Type II error rates observed across a range of window sizes for optimization $w_o$. For a window size of $w_o = 130$ we see a minimum in type II error rate across all type I rates considered. Smaller validation sizes $w_v$ are typically associated with a smaller type II error."}
if (!file.exists("../data/cvcs2.RDS")) {
files <- dir("../data/crossvalidate-cs2/")
cvcs2 <- data.frame()
for (file in files) {
  tmp <- readRDS(file.path("../data/crossvalidate-cs2/",file))
  cvcs2 <- rbind(cvcs2, tmp)
}
cvcs2$coarse <- cvcs2$coarseness
cvcs2$method <- "CS2"
saveRDS(cvcs2, file = "../data/cvcs2.RDS")
} else cvcs2 <- readRDS("../data/cvcs2.RDS")

@@

>>>>

```{r , fig.height = 3, fig.width = 7.5, out.width='0.9\\textwidth', fig.cap="Type II error rates observed across a range of window sizes for optimization $w_o$. For a window size of $w_o = 130$ we see a minimum in type II error rate across all type I rates considered. Smaller validation sizes $w_v$ are typically associated with a smaller type II error."}
if (!file.exists("../data/cvcs2.RDS")) {
files <- dir("../data/crossvalidate-cs2/")
cvcs2 <- data.frame()
for (file in files) {
  tmp <- readRDS(file.path("../data/crossvalidate-cs2/",file))
  cvcs2 <- rbind(cvcs2, tmp)
}
cvcs2$coarse <- cvcs2$coarseness
cvcs2$method <- "CS2"
saveRDS(cvcs2, file = "../data/cvcs2.RDS")
} else cvcs2 <- readRDS("../data/cvcs2.RDS")

@@

## Type 2 errors: CS1 vs CS2

\autoref{type2} gives an overview of type 2 error rates of methods CS1 and CS2 for different significance levels $\alpha$. Method CS2 is outperforming CS1 significantly in every instance.

```{r type2, fig.height = 3, fig.width = 7.5, out.width='0.9\\textwidth', fig.cap="Type II error rates observed across a range of window sizes for optimization $w_o$. For a window size of $w_o = 130$ we see a minimum in type II error rate across all type I rates considered. Smaller validation sizes $w_v$ are typically associated with a smaller type II error."}
ggerrors
```
